Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-02-08 Journal1/paper2TNSM/pr.tex
Add other questions

\textcolor{magenta}{ We can reduce the complexity of our delay calculation and enhance the performance of our solution by eliminating propagation and transmission delays to focus on obtaining the optimal number of VNF. 
In this paper, we focus only on the processing delays to find the optimal number of VNFs, and we consider the other two delays are fixed for simplification;
Since the distance between the O-RU to O-DU is about 10 km and also the distance between O-DU and O-CU is about 80 km. Moreover, the distance from O-CU to the network should not exceed 200 km \cite{oranD1}. so, the propagation delay is about $T^{\text{pro}} = (10 + 80 + 200)\times 10^3 /(3\times 10^8) < 1ms $. Since, fronhaul, midhaul and backhaul are fiber optics, c is the speed of light. Also, due to the use of the edge technique in O-DU or O-CU for users with low latency, this amount of latency is greatly reduced. But we do not focus on edge processing in this paper.
In URLLC and mMTC, the mean packet size can be between 20 to 32 byte; Also, the minimum data rate is assume to be $46 bits/sec/Hz \times BW (180 KHz)$. So the transmission delay from O-RU to O-DU is about $T^{fr,t} = \frac{20\times 8}{46 \times 180 \times 10^3} < 2 us$. As a result, the $T^{fr,t} \approx T^{mid,t} \approx T^{b,t}$. for eMBB, the packet size can be 100 times larger and the delay is not exceed the 0.6ms.  
}

@@

\textcolor{olive}{The processing delay can be considered an M/M/1; since the number of arrival packets in the system is enormous, and the packets are independent. Moreover, the impact of a single packet on the system's performance is minimal. Also, the queue discipline will be first-in, first-out (FIFO), and the arrival packet is assumed to follow a Poisson process. We also suppose that service times are exponentially distributed. In addition, we assume that the arrival packets of each service have the same priority, and we consider priority between services. Because in this system, it is also assumed that the users of a service have the same priority, so their sent packages also have an equal priority over each other. Because the services are isolated, this priority within a service does not invalidate the queue assumption. Also, one service's priority over another can be higher, affecting the optimization.} 
\subsection{VNF Power}
%{\color{red} Assume the power consumption of the baseband processing, the VNFs cost of a slice $s$ is depicted as $\phi_{s}$. Sentence has no meaning.} 
Assume the power consumption of each VNF in each logical node (the O-DU, the O-CU, and the UPF) in the slice s, is depicted as $\phi_{s}^d$, $\phi_{s}^c$, and $\phi_{s}^u$, respectively.

@@

Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{s}^{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
So, a lower bound for \eqref{eq11} is given that is a concave function.
\begin{subequations}
\begin{alignat}{4}
\bar{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \bar{\rho}_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\bar{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\bar{\mathcal{R}}_{u(s_j,i)}^{r}\\ 
 \hat{\zeta}_{u(s_j,i)}^{k} =& log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
 \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}.
\end{alignat}
\end{subequations}
Without loss of generality, assume that UPF, O-CU and O-DU use the processors with the same processing capability. We notice that it makes the formulation simpler. However, loosing this assumption does not change the formulation significantly and the problem can be solved in the same manner. Therefore, we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,
the mean arrival data rate of the UPF layer for a service $s$ ($\alpha_{s}^U$) is equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). So $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. Again, this assumption only simplifies the notations and loosing it does not make the solution inefficient.
These assumptions lead to having the same processing power for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.
As a result, we have $M_s = M_s^u = M_s^c = M_s^d $.
Using the above assumption, we have $T^{DU}_{s} = T^{CU}_{s} = T^{UPF}_{s}$ and we have 
$T^{\text{proc}}_{s} =  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}$. So,
$T^{\text{proc}}_{s}=  T^{RU}_{s} + 3\times T^{DU}_{s}.$  
%\begin{equation}
%\begin{split}
%T^{\text{proc}}_{s} &=  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s} \\
%                     &=  T^{RU}_{s} + 3\times T^{DU}_{s}.
%\end{split}
%\end{equation}

\textcolor{violet}{Since problem \eqref{problem} is mixed-integer nonlinear programming with two integer constraints which are a binary variable ($e$ shows the PRB assignment) and an integer variable ($M_s$ indicate the number of VNFs in slice s), the problem is NP-hard. Solving the problem is complex. To solve the problem by inspiring Stackelberg, we reformulate the equation \eqref{c16} to reduce one of the variables ($M_s$) that can be solved after obtaining the rate of UEs ($M_s$ is similar to followers in Stackelberg Competition and power and PRB assignment is similar to leader). So, the new problem has two variables of power and PRB assignment. This new problem is convex by relaxing the binary variable (PRB assignment) and can be solved by the Lagrangian function. After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs.}

@@

We consider 25 PRBs are used in the network and the packet size is equal to 20 bytes.

>>>>

\textcolor{magenta}{Considering propagation and transmission delays is straightforward to add to the system, but we did not consider them for better presentation and focus on obtaining the optimal number of VNF.
In this paper, we focus only on the processing delays to find the optimal number of VNFs, and we consider the other two delays are fixed for simplification;
The propagation delay is considered when each O-RU can connect to the number of O-DUs and can select to connect to which O-DU based on the route, capacity, and priority (Also, the connections of O-DUs to O-CUs is the same as O-RU to O-DU). Therefore, different routes are added to the system to solve the routing problem, but we do not consider it since it changes the model and does not fit in this model. So, the connection between O-RUs to O-DUs is fixed and transparent. As a result, the propagation delay is fixed and does not affect the optimization problem.
The following is a brief calculation of propagation delay.
Since the distance between the O-RU to O-DU is about 10 km and also the distance between O-DU and O-CU is about 80 km. Moreover, the distance from O-CU to the network should not exceed 200 km \cite{oranD1}. so, the propagation delay is about $T^{\text{pro}} = (10 + 80 + 200)\times 10^3 /(3\times 10^8) < 1ms $. Since fronhaul, midhaul, and backhaul are fiber optics, c is the speed of light. Also, due to the edge technique in O-DU or O-CU for users with low latency, this amount of latency is greatly reduced. But we also do not focus on edge processing in this paper.
The following is a brief calculation of transmission delay to show that it does not affect the optimization since it has such a small amount.
In URLLC and mMTC, the mean packet size can be between 20 to 32 byte; Also, the minimum data rate is assume to be $46 bits/sec/Hz \times BW (180 KHz)$. So the transmission delay from O-RU to O-DU is about $T^{fr,t} = \frac{20\times 8}{46 \times 180 \times 10^3} < 2 us$. As a result, the $T^{fr,t} \approx T^{mid,t} \approx T^{b,t}$. for eMBB, the packet size can be 100 times larger and the delay is not exceed the 0.6ms.  
}

@@

\textcolor{olive}{The processing delay can be considered an M/M/1; since the number of arrival packets in the system is enormous, and the packets are independent. Moreover, the impact of a single packet on the system's performance is minimal. Also, the queue discipline will be first-in, first-out (FIFO), and the arrival packet is assumed to follow a Poisson process. The system's clock is constant, and the size of the tasks is not fixed. So, we suppose that service times are exponentially distributed \cite{QS}. In addition, we assume that the arrival packets of each service have the same priority, and we consider priority between services, not between UEs of one service. Because we assumed that the UEs of a service have the same priority, their sent packets also have an equal priority. Also, the services are isolated, and this priority does not invalidate the queue assumption. Furthermore, one service's priority over another can be higher, affecting the whole optimization and not queue formulation since the UEs in each service have the same priority, and each service has its processing delay independent of other services.} 
\subsection{VNF Power}
%{\color{red} Assume the power consumption of the baseband processing, the VNFs cost of a slice $s$ is depicted as $\phi_{s}$. Sentence has no meaning.} 
Assume the power consumption of each VNF in each logical node (the O-DU, the O-CU, and the UPF) in the slice s, is depicted as $\phi_{s}^d$, $\phi_{s}^c$, and $\phi_{s}^u$, respectively.

@@

Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{s}^{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
So, a lower bound for \eqref{eq11} is given that is a concave function.
\begin{subequations}\label{lb1}
\begin{alignat}{4}
\bar{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \bar{\rho}_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\bar{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\bar{\mathcal{R}}_{u(s_j,i)}^{r}\\ 
 \hat{\zeta}_{u(s_j,i)}^{k} =& log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
 \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}.
\end{alignat}
\end{subequations}
Without loss of generality, assume that UPF, O-CU and O-DU use the processors with the same processing capability. We notice that it makes the formulation simpler. However, loosing this assumption does not change the formulation significantly and the problem can be solved in the same manner. Therefore, we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,
the mean arrival data rate of the UPF layer for a service $s$ ($\alpha_{s}^U$) is equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). So $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. Again, this assumption only simplifies the notations and loosing it does not make the solution inefficient.
These assumptions lead to having the same processing power for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.
As a result, we have $M_s = M_s^u = M_s^c = M_s^d $.
Using the above assumption, we have $T^{DU}_{s} = T^{CU}_{s} = T^{UPF}_{s}$ and we have 
$T^{\text{proc}}_{s} =  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}$. So,
$T^{\text{proc}}_{s}=  T^{RU}_{s} + 3\times T^{DU}_{s}.$  
%\begin{equation}
%\begin{split}
%T^{\text{proc}}_{s} &=  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s} \\
%                     &=  T^{RU}_{s} + 3\times T^{DU}_{s}.
%\end{split}
%\end{equation}

\textcolor{violet}{Although the problem is feasible and it has feasibility points that are discussed in subsection \ref{fr}, it is not convex and difficult to solve. Since problem \eqref{problem} is mixed-integer nonlinear programming with two integer constraints which are a binary variable ($e$ shows the PRB assignment) and an integer variable ($M_s$ indicate the number of VNFs in slice s), the problem is NP-hard. Solving the problem is complex. To solve the problem by inspiring Stackelberg, we reformulate the equation \eqref{c16} to reduce one of the variables ($M_s$) that can be solved after obtaining the rate of UEs ($M_s$ is similar to followers in Stackelberg Competition and power and PRB assignment is similar to leader). So, the new problem has two variables of power and PRB assignment. This new problem is convex by relaxing the binary variable (PRB assignment) and estimating the lower bounds in equation \eqref{lb1} because the objective function and constraints of the problem are convex and can be solved by the Lagrangian function. After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs.}

@@

We consider 25 PRBs are used in the network and the packet size for mMTC is equal to 20 bytes, and for URLLC is equal to 32 bytes.
